Beyond clines: lineages and haplotype blocks in hybrid zones

### 2016-04-26 drafts/hybrid_zone.tex
save stuff for new fig

\begin{figure}
\includegraphics{figs/blocksAlongChromAncBConditioningHighRes.pdf}
\caption{\textbf{Normalized mean enclosing block length}, $\bar l_B(m,x)$, along a simulated chromosome of length $1M$ with selected locus of $s=0.01$ at position $0.5M$ in a hybrid zone of $T=1000$. 
    Here each line shows $\bar l_B(m,x)$, in a given deme some distance from the zone center. % , and is normalized by dividing by mean $l_B(m)$ along the chromosome within the deme. 
    Chromosome were sampled across the hybrid zone, which consists of 50 demes, each containing 500 diploid individuals. 
    The same simulation and statistic are shown in Fig.~\ref{Fig:blockLengths}, on coarser genomic scale.
}\label{Fig:blockLengthsZoom}
\end{figure}

@@

Our results suggest that the statistic $l(x,m)$ 
-- the mean genetic length of ancestry surrounding a site of a given lineage --
could help identify selected loci in hybrid zones. 
The ratio of mean adjacent block lengths, $C(x,m)$, alsot shows a very sharp peak at the selected site,
suggesting that, despite the fact that haplotypes surrounding incompatibilities might be quite long, 
genome scans may have the power to extract fine-grained regions near selected loci from the large chunks of ancestry that will often flank these regions.

>>>>

\begin{figure}
\includegraphics{figs/s0point01_BlocksAlongChromAncBConditioning.pdf}
\caption{\textbf{Normalized mean enclosing block length}, $\bar l_B(m,x)$, along a simulated chromosome of length $1M$ with selected locus of $s=0.01$ at position $0.5M$ in a hybrid zone of $T=1000$. 
    Here each line shows $\bar l_B(m,x)$, in a given deme some distance from the zone center. % , and is normalized by dividing by mean $l_B(m)$ along the chromosome within the deme. 
    Chromosome were sampled across the hybrid zone, which consists of 50 demes, each containing 500 diploid individuals. 
    The same simulation and statistic are shown in Fig.~\ref{Fig:blockLengths}, on a coarser genomic scale.
}\label{Fig:blockLengthsZoom}
\end{figure}

@@

Our results suggest that the statistic $l_B(x,m)$ 
-- the mean genetic length of ancestry surrounding a site of a given ancestry --
could help identify selected loci in hybrid zones. 
The ratio of mean adjacent block lengths, $C(x,m)$, also shows a very sharp peak at the selected site,
suggesting that, despite the fact that haplotypes surrounding incompatibilities might be quite long, 
genome scans may have the power to extract fine-grained regions near selected loci from the large chunks of ancestry that will often flank these regions.
